Local wind regime induced by the presence of giant linear dunes.

### 2022-01-04 Paper/main.tex
Commit before sending to Clement and Philippe

As a flow encounters an obstacle, different interactions can arise depending on the different time and length scales involved. In the case of atmospheric flows, this mainly depends on the part of the atmosphere, schematically composed of a turbulent boundary layer topped by a stably stratified one, with which the obstacle interacts \citep{Stull1988}.
%
At the largest scale, the feedback of mountains on the stratified part results in wave generation as well as significant wind disturbances, such as downslope winds in the lee side \citep{Duran1990}. Inside the boundary layer, the interaction between a turbulent flow and hilly surfaces is for example key to the understanding ocean surface wind-driven waves~\citep{Sullivan2010}, or eolian bedforms in desert \citep{Courrech2015}.

@@

In the case of aeolian bedforms, the measurements mentioned above were made on dunes a few meters high only. The resulting wind disturbances have then been shown to significantly impact the sediment pathways of the system \citep{Hesp2015}, but also to affect the collective behaviour of dune populations trough long-range interactions \citep{Bacik2020}.
%
However, eolian dunes coexists in sand seas at different scales, each representative of their different evolution stages, from emergence at twenty meters wavelengths to giant size, corresponding to kilometric wavelengths and heights of several dozen meters \citep{McKee1979}. Quantifying these two effects for giant dunes is then all the more important for several reasons.
%
First, larger wind disturbances are expected from larger obstacles.
%
Second, the flow--structure coupling is not straightforward due to vertical structure of the atmosphere with which the giant dunes interact due to their sizes \citep{andreotti2009}.
%
Finally, the morphodynamics of aeolian bedforms are strongly dependent on the wind regime~\citep{Livingstone1996}. Thus, small-scale bedforms are sensitive to wind disturbances induced by larger-scale bedforms. This has been demonstrated for impact ripples on dunes \citep{Howard1977,Hood2021}, but has never been studied for medium-scale dunes near giant dunes.

>>>>

As a flow encounters an obstacle, different interactions can arise depending on the different time and length scales involved. In the case of atmospheric flows, this mainly depends on the part of the atmosphere, schematically composed of a turbulent boundary layer topped by a stably stratified one, with which the obstacle interacts \citep{Stull1988}.
%
At the largest scale, the feedback of mountains on the stratified free atmosphere results in wave generation as well as significant wind disturbances, such as downslope winds in the lee side \citep{Duran1990}. Inside the boundary layer, the interaction between a turbulent flow and hilly surfaces is for example key to the understanding ocean surface wind-driven waves~\citep{Sullivan2010}, or eolian bedforms in desert \citep{Courrech2015}.

@@

In the case of aeolian bedforms, the measurements mentioned above were made on dunes a few meters high only. The resulting wind disturbances have then been shown to significantly impact the sediment pathways of the whole system \citep{Hesp2015}, but also to affect the collective behaviour of dune populations trough long-range interactions \citep{Bacik2020}.
%
However, eolian dunes coexists in sand seas at different scales, each representative of their different evolution stages, from emergence at twenty meters wavelengths to giant size, corresponding to kilometric wavelengths and heights of several dozen meters \citep{McKee1979}. Quantifying these two effects for giant dunes is then all the more important for several reasons.
%
First, larger wind disturbances are expected from larger obstacles.
%
Second, the flow--structure coupling is not straightforward due to vertical structure of the atmosphere with which the giant dunes interact due to their sizes \citep{andreotti2009}.
%
Finally, the morphodynamics of aeolian bedforms are strongly dependent on the wind regime~\citep{Livingstone1996}. Thus, small-scale bedforms are sensitive to wind disturbances induced by larger-scale bedforms. This has been demonstrated for impact ripples on dunes \citep{Howard1977,Hood2021}, but has never been studied for medium-scale dunes near giant dunes.
